BEX3012 Project Analysis

### 2017-06-18 Internship/EmotionsAnalysis.Rmd
Presentation Changes

###
Join emotions for each face
J2: Table of FileNames and associated dominant emotion
```{r combined}
S1 <- select(SBP1, FileName = aname , SEmotion = Emotion)
S2 <- select(MEP1, FileName, MEmotion = Emotion)
S3 <- select(GEP1, FileName, GEmotion = Emotion)
J1 <- full_join(S1, S2, by = "FileName")
J2 <- full_join(J1, S3, by = "FileName")

@@

Player Subsetting
```{r DisplayFaces}
AKimgsG<-GEP %>% filter(player2=="ACornet")
AKimgsG<-AKimgsG %>% filter(detect=="Player")
AKlist <- as.list(AKimgsG$FileName)
length(AKlist)

DisplayFaces(AKlist)

>>>>

###
Join emotions for each face
J2: Table of FileNames and associated dominant emotion
```{r combined}
S0 <- select(GFP, FileName, type)
S1 <- select(SBP1, FileName = aname , SEmotion = Emotion)
S2 <- select(MEP1, FileName, MEmotion = Emotion)
S3 <- select(GEP1, FileName, GEmotion = Emotion)
J <- full_join(S0, S1, by = "FileName")
J1 <- full_join(J, S2, by = "FileName")
J2 <- full_join(J1, S3, by = "FileName")

J2 <- select(J2, FileName, Skybiometry = SEmotion,
             Microsoft = MEmotion, Google = GEmotion)

write.csv(J2, "DominantEmotions.csv", row.names = FALSE)

@@

Player Subsetting
```{r DisplayFaces}
AKimgsG<-GEP %>% filter(player1=="NDjokovic")
AKimgsG<-AKimgsG %>% filter(detect=="Player")
AKlist <- as.list(AKimgsG$FileName)
length(AKlist)
AKlist[6]
DisplayFaces(AKlist)
